A function--sheaf dictionary for algebraic tori over local fields

### 2014-01-21 shanghai.tex
Improved the language around the example at the end of Part 1.

For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
corresponding to $\chi$ under Theorem~\ref{thm:snake}.
Then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
bounded.  If $\chi(1) = 1+\ell$, then the image of $\chi$ is bounded but not finite.  For
the corresponding quasicharacter sheaf $\qcs{L}$, the stalk at the component $1$ is defined
by a pro-\'etale cover rather than an \'etale cover and thus $\qcs{L}$ is not finite.

>>>>

Using Corollary~\ref{cor:bounded-and-finite} we can easily see that, in general, neither of the full subcategories
$\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.
For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
If $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = \ell$ 
and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class 
corresponding to $\chi$ under Theorem~\ref{thm:snake},
then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
bounded.  
On the other hand, if $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = 1+\ell$ 
and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class 
corresponding to $\chi$ under Theorem~\ref{thm:snake},
then $\qcs{L}$ is a bounded quasicharacter sheaf but not a finite quasicharacter sheaf
since the image of $\chi$ is bounded but not finite.
In this latter case the stalk of $\qcs{L}$ at the component $1$ is defined
by a pro-\'etale cover rather than an \'etale cover.
